Abstract Binding Trees

### 2015-10-24 paper.tex
Add a TODO comment
Clarification (really close #10)

\newcommand\ArrDom[1]{\mathsf{dom}(#1)}
\newcommand\Match[2]{\IMode{#1}\equiv\OMode{#2}}

@@

Declaring a new assignable consists in providing an initial value, and an
expression with a free symbol (which shall represent the assignable in scope).
Note that the functoriality of $\Operators$ guarantees for any renaming
$\Of{\varrho}{\Upsilon\to\Upsilon'}$ a restriction map $\Restriction{\varrho}$
such that $\IsOperator{\Upsilon'}{\Restriction{\varrho}(\vartheta)}{a}$ when
$\IsOperator{\Upsilon}{\vartheta}{a}$. In particular, the renaming
$\Upsilon,u\mapsto\Upsilon,v$ shall take $\mathsf{get}[u]$ to
$\mathsf{get}[v]$.

@@

>>>>

\newcommand\ArrId{\mathbf{id}}
\newcommand\Match[2]{\IMode{#1}\equiv\OMode{#2}}

@@

Declaring a new assignable consists in providing an initial value, and an
expression with a free symbol (which shall represent the assignable in scope).
Note that the functoriality of $\Operators$ guarantees for any renaming
$\Of{\varrho}{\Upsilon\to\Upsilon'}$ and $\Of{f}{a\to a'}$, a restriction map
$\Restriction{\Pair{\varrho}{f}}$ such that
$\IsOperator{\Upsilon'}{\Restriction{\Pair{\varrho}{f}}(\vartheta)}{a}$ when
$\IsOperator{\Upsilon}{\vartheta}{a'}$. Because the category
$\Discrete{\Arities}$ is discrete and has only identity arrows, we will often
write $\Restriction{\varrho}$ to mean $\Restriction{\Pair{\varrho}{\ArrId}}$
through an abuse of notation. In particular, the renaming
$\Upsilon,u\mapsto\Upsilon,v$ shall take $\mathsf{get}[u]$ to
$\mathsf{get}[v]$.

@@

%%% TODO: show that renaming preserves wellformedness
